Lyman-$\alpha$ photons through rotating outflows

### 2018-03-29 paper/paper.tex
edit

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm V_{\mathrm{rot}}\else $V_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm V_{\mathrm{out}}\else $V_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode\mathrm \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

The case for outflows as traced in the \lya\ line is much bettwe
stablished.
There are abundance cases \lya line profiles with a single peak
redwards from the line's center. 
In other cases there is a double peak but the peak on the red side is
stronger \citep[e.g.][]{2010ApJ...717..289S,Erb14,Trainor16}.  
This has been readily explained as the consequence of multiple \lya photon
scatterings through an homogeneous outflowing shell of neutral Hydrogen
\citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.

@@

\subsection{Qualitative Trends}
\label{sec:qualitative}
Figure \ref{fig:doppler_shift} summarizes the most important trends of
our simulations. 
The six panels correspond to $\tau=10^6$ and a viewing angle of
$\theta =90^{\deg}$, that is perpendicular to the rotation axis of the
galaxy. 
In every panel the thin black line corresponds to the pure outflow
solution (i.e. without rotation). 
From top to bottom we see the effect of increasing the outflow
velocity, which is the expected increasing asymmetry towards the red
peak.

@@

In Figure \ref{fig:angle_influence} we show the same results as in
Figure \ref{fig:doppler_shift} but for a viewing angle of $\theta =
90^{\deg}$, that is parallel to the rotation axis. 
In this case we see that the effect of rotation is very hard to see. 
As \ref{Garavito14} showed, pure rotation introduces a strong
dependence with viewing angle, a trend that we find also holds for
rotation mixed with ouflows.

@@

After finding the qualitative influence of the different parameters.

We evaluate the effects of increasing outflows velocity at fixed
values for the optical depth and rotational velocity.
Figure \ref{fig:varying_outflow_small} summarizes its behavior
(for a largest range see Figure \ref{fig:varying_outflow}).
All plots correspond to the same rotation velocity of
$\vrot=50$\kms, rows have constant optical depth and columns
have constant outflows velocity.

Figure \ref{fig:doppler_shift} displays this Doppler shift for six different
configurations with a fixed optical depth \tauh. In each cell of the grid
there is a \lya spectrum for a galaxy with only outflows and two \lya spectra
for the galaxy with outflows and rotation: one obtained from the radiative
transfer simulation and the other obtained from the Doppler shifting of the
non-rotating galaxy.

% Esta figura deberia tener 2 x 2 vinetas. vrot=50.
% cada panel tiene una curva para theta=0, 45, 90.
% | tau=1E5, vout=25, | tau=1E5, vout=75 |
% | tau=1E6, vout=25, | tau=1E6, vout=75 |
%\begin{figure*}
%\begin{center}
%\includegraphics[width=0.90\textwidth]{./figures/results/varying_outflow_small}
%\end{center}
%\caption{\textbf{Spectra for fixed rotational velocity:} We fixed $\vrot=50$\kms.  We vary \vout in%creasing from left to right, \tauh increasing from top to
			 bottom, and $\theta$ according to the legend.
%\label{fig:varying_outflow_small}}
%\end{figure*}

\subsection{Doppler Shifts to Include Rotational Effects}

% Esta figura deberia tener 3 x 2 viñetas. tau=10E6.
% cada panel tiene una curva para no rotation, rotation (radiative transfer)
% y rotation (doppler)
% |vrot=50, vout=5,  | vrot=100, vout=5,  |
% |vrot=50, vout=25, | vrot=100, vout=25, |
% |vrot=50, vout=50, | vrot=100, vout=50, |

In order to compare the line created with the radiative transfer (RT) process that
involves the rotation and the line with only outflows that is Doppler
shifted (DS), we calculate three main characteristics for each spectrum. We
measure the line's standard deviation (STD), skewness (SKW) and bimodality (BI) 
for both RT's and DS's approaches. We use the definitions in Eqs. \ref{eq:std}, 
\ref{eq:skw}, \ref{eq:bi} for each value \citep{kokoska1999}.

@@

\begin{equation}
\label{eq:bi}
\mathrm{BI} = \mathrm{KURTOSIS} - \mathrm{SKW}^2 = \frac{m_4}{m_2^{2}} - \frac{m_3^2}{m_2^{3}},
\end{equation}

where each $m_i$ is the i-th moment about the mean. The STD has velocity units and 
quantifies the dispersion of the line's velocity: the larger it is, the wider the line. 
The SKW is adimensional and quantifies the peaks' asymmetry: if it is $>0$ the left peak is 
taller and if it is $<0$ the right peak is taller. The BI is adimensional and
quantifies if the line has 1 or 2 peaks: it is  always $\geq 1$ \citep{Pearson1929} and the closer it is to 1, the more bimodal is the line (i.e. has 2 peaks).

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}
%=========================================================================
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage[dvips]{epsfig}
\usepackage{epsfig}
\usepackage{color}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{bm}
%Non reposionated tables
\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
\newcommand{\vrot}{\ifmmode\mathrm v_{\mathrm{rot}}\else $v_{\mathrm{rot}}$~\fi}
\newcommand{\vout}{\ifmmode\mathrm v_{\mathrm{out}}\else $v_{\mathrm{out}}$~\fi}
\newcommand{\tauh}{\ifmmode\mathrm \tau_{\mathrm{H}}\else $\tau_{\mathrm{H}}$~\fi}
\newcommand{\vth}{\ifmmode\mathrm v_{\mathrm{th}}\else $v_{\mathrm{th}}$~\fi}

@@

The case for outflows as traced in the \lya\ line is much better
stablished.
In many cases the \lya line profiles has a single peak
redwards from the line's center, in other cases there is a double peak
but the peak on the red side is stronger
\citep[e.g.][]{2010ApJ...717..289S,Erb14,Trainor16}.   
These features been readily explained as the consequence of multiple
\lya photon scatterings through an homogeneous outflowing shell of
neutral Hydrogen
\citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.

@@

\subsection{Qualitative Trends}
\label{sec:qualitative}
Figure \ref{fig:doppler_shift} summarizes the most important trends of
our simulations. 
The six panels correspond to $\tau=10^6$ and a viewing angle of
$\theta =90^{\circ}$, that is perpendicular to the rotation axis of the
galaxy. 
In every panel the thin black line corresponds to the pure outflow
solution (i.e. without rotation). 
From top to bottom we see the effect of increasing the outflow
velocity, which is the expected increasing asymmetry towards the red
peak.

@@

In Figure \ref{fig:doppler_shift_theta_0} we show the same results as
in Figure \ref{fig:doppler_shift} but for a viewing angle of $\theta =
90^{\circ}$, that is parallel to the rotation axis. 
In this case we confirme the result presented by \ref{Garavito14}
showed, namely that pure rotation introduces a strong dependence with
viewing angle, a trend that we find also holds for rotation mixed with
ouflows.

@@

After finding the quantitative influence of the different parameters we
move onto a qualilitative study.
To do this we summarize the line morphology by four different
characteristics: standard deviation (STD), skewness (SKW), bimodality
(BI) and valley/peak ration.
These quantities are defined by the following equations \citep{kokoska1999}.:

@@

\begin{equation}
\label{eq:bi}
\mathrm{BI} = \mathrm{KURTOSIS} - \mathrm{SKW}^2 = \frac{m_4}{m_2^{2}} - \frac{m_3^2}{m_2^{3}},
\end{equation}
%
where each $m_i$ is the i-th moment about the mean. 
The STD has velocity units and quantifies the dispersion of the line's
velocity: the larger it is, the wider the line.  
The SKW is adimensional and quantifies the peaks' asymmetry. 
In the case of a bimodal distributio 
$SKW>0$ the blue peak is taller and for $SWK<0$ the right peak is
taller. The BI is adimensional and quantifies if the line has 1 or 2 peaks: it is  always $\geq 1$ \citep{Pearson1929} and the closer it is to 1, the more bimodal is the line (i.e. has 2 peaks).
